Article Title

### 2014-06-25 plos.tex
Minor corrections. This was sent to co-authors for review before resubmission.

Improved estimation of the correlation matrix is beneficial in itself. For example, improved estimates can be used to optimize  decoding of the population activity \cite{Friedman:1989}. But reduced estimation error is not the only benefit of regularization.  The estimation improvement is greatest when the structure imposed by regularization limits the solution space while still allowing representation of the dominant dependencies in the data. Therefore, finding the most efficient among many regularized estimators leads to insights about the system itself: the structure of the most efficient estimator is a parsimonious representation of the regularities in the data.

@@

Given a set of observations $\{x(t): t\in T$\} of population activity, where $x(t)$ is a $p\times 1$ vector of firing rates in time bin $t$, and an independent unbiased estimate $\bar x$ of the mean activity, the \emph{sample covariance matrix},
\begin{equation}\label{eq:sample}
	C_{\sf sample} = \left[\mbox{cov}\left(x(t)\right)\right]_{t\in T} =\frac 1 n \sum\limits_{t\in T} (x(t)-\bar x)(x(t)-\bar x)^\T,
\end{equation}
where $n$ is the size of $T$, yields an unbiased estimate of the covariance matrix so that $\E{C_{\sf sample}}=\Sigma$.

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics{./figures/Figure01.pdf}
    \end{center}
    \caption{{\bf Regularized estimators whose structure matches the true structure in the data are more efficient.}
    {\bf Row 1.} Graphical representations of the target estimates of the four respective regularized covariance matrix estimators.  Recorded neurons are represented by green spheres and latent units by light-shaded spheres.  Edges represent non-zero partial correlations, \ie \sq{interactions}.
        {\bf Row 1, A}.  For estimator $C_{\sf diag}$, the target estimate is a diagonal matrix, which describes systems that lack linear dependencies. 
        {\bf  Row 1, B.} For estimator $C_{\sf factor}$, the target estimate is a factor model (low-rank matrix plus a diagonal matrix), representing systems in which correlations arise due to common input from latent units. 
        {\bf  Row 1, C}. For estimator $C_{\sf sparse}$, the covariance matrix is approximated as the inverse of a sparse matrix. This approximation describes systems in which correlations arise from a sparse set of  linear associations between the observed units. 
        {\bf  Row 1, D}.  For estimator $C_{\sf sparse+latent}$, the covariance matrix is approximated as the inverse of the sum of a sparse matrix and a low-rank matrix. This approximation describes a model wherein correlations arise due to sparse associations between the recorded cells \emph{and} with several latent units. \\
{\bf Row 2:} Examples of $50\times 50$ correlation matrices corresponding to each structure: {\bf A.} the diagonal correlation matrix, {\bf B.} a factor model with four latent units, {\bf C.}  a correlation matrix with 67\%  off-diagonal zeros in its inverse, and {\bf  D.} a correlation matrix whose inverse is the sum of a rank-3 (\ie three latent units) matrix and a sparse matrix with 76\% off-diagonal zeros. 
\\
{\bf Row 3:} Sample correlation matrices calculated from samples of size $n=500$ drawn from simulated random processes with respective correlation matrices shown in Row 2.  The structure of the sample correlation matrix is difficult to discern.
\\
{\bf Row 4:} Correlation matrix estimates computed by estimators with matching structure from the same data as the sample correlation matrices in Row 3. The regularized estimates are closer to the truth than the sample correlation matrices.
\\
{\bf Row 5:} Excess losses (Eq.~\ref{eq:loss}) for the five estimators as a function of sample size. The error bars indicate the standard error of the mean based on 30 samples.  Estimators with structure that matches the true model converged to zero faster than the other estimators. Some exceptions occur when the sample is too small to reveal the structure in the data. In these cases estimators with simpler structures can be more efficient than estimators with true structure.
\\
{\bf Row 6:} Cross-validation losses for the five estimators relative to the matching estimator. Error bars indicate the standard error of the mean based on 30 samples.
    }
    \label{fig:1}
\end{FPfigure}

@@

We drew 30 independent samples of sizes $n=250$, 500, 1000, 2000, and 4000 from each model and computed the \emph{excess loss} $\loss{C,\Sigma}-\loss{\Sigma,\Sigma}$ for each of the five estimators.  The hyperparameters of the regularized estimators were optimized by nested cross-validation using only the data in the sample.  All the regularized estimators produced better estimates (lower excess loss) than the sample covariance matrix.  However, estimators whose structure matched the true model outperformed the other estimators (\figref{1}{\,row 5}).  Note that when the ground truth had zero correlations (Column A), $C_{\sf factor}$ performed equally well to $C_{\sf diag}$ because it correctly identified zero factors and only estimated the individual variances. Similarly, when the number of latent units was zero (Column C), $C_{\sf sparse+latent}$ performed equally well to $C_{\sf sparse}$ because it correctly identified zero latent units.

@@

To test this hypothesis, we computed the relative cross-validation loss of estimators  $C_{\sf sample}$, $C_{\sf diag}$, $C_{\sf factor}$, and $C_{\sf sparse}$ with respect to $C_{\sf sparse+latent}$ in $n=27$ imaged sites in 14 mice.  The hyperparameters of each estimator were optimized by nested cross-validation (See Methods). Indeed, the sparse+latent estimator outperformed the other estimators (Fig.~\ref{fig:3}). The respective median differences of the cross-validation loss were 0.039, 0.0016, 0.0029, and 0.0059 nats/cell/bin, significantly greater than zero ($p<10^{-2}$ in each comparison, $n=27$ sites in 14 mice, Wilcoxon signed rank test).

@@

First, we analyzed how correlations and connectivity depended on the difference in preferred orientations ($\Delta ori$) of pairs of significantly ($\alpha=0.05$) tuned cells. The partial correlations decayed more rapidly with $\Delta ori$ than did sample correlations ($p<10^{-9}$ in each of the five sites, two-sample $t$-test on the linear regression coefficients). Positive connectivity decreased rapidly with $\Delta ori$ ($p<0.005$ in each of the five sites, $t$-test on the logistic regression parameter) whereas negative connectivity did not decrease (\figref{6}{D}): The slope in the logistic model of connectivity with respect to $\Delta ori$ was significantly higher for positive than for negative interactions ($p<0.04$ in each of the five sites, two-sample $t$-test on the logistic regression parameters).

Second, we compared how correlations and connectivity depended on the physical distance separating pairs of cells. We distinguished between lateral distance, $\Delta x$, in the plane parallel to the pia, and vertical distance, $\Delta z$, orthogonal to the pia.  When considering the dependence on $\Delta x$, the analysis was limited to cell pairs located at the same depth with $\Delta z < 30\,\mu\mbox{m}$; conversely, when considering the dependence on $\Delta z$, only vertically aligned cell pairs with $\Delta x < 30\,\mu\mbox{m}$ were included. Again, the partial correlations decayed more rapidly both laterally and vertically than sample correlations ($p<10^{-6}$ in each of the five sites, for both lateral and vertical distances, two-sample $t$-test on the linear regression coefficients). 
Positive connectivity decayed rapidly with distance ($p<10^{-6}$ in each of the five sites for positive interactions and $p<0.05$ for negative interactions, $t$-test on the logistic regression parameter) (\figref{6}{E}), so that cells separated laterally by less than 25 $\mu\mbox{m}$ were 3.2 times more likely to be connected than cells separated laterally by more than 150 $\mu\mbox{m}$. Although the positive connectivity appeared to decay faster with vertical than with lateral distance, the differences in slopes of the respective logistic regression models was not significant with available data. The negative connectivity decayed significantly slower with distance in the available range (\figref{6}{E and F}): The slope in the respective logistic models with respect to the lateral distance was significantly higher for positive than for negative connectivities ($p<0.05$ in each of the five sites, two-sample $t$-test on the logistic regression parameters).

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure06.pdf}
    \end{center}
    \caption{{\bf Dependence of sample correlations, regularized partial correlations, and inferred connectivity of the $C_{\sf sparse+latent}$ estimator on the differences in preferred orientations, $\Delta ori$, and physical distances, $\Delta x$ and $\Delta z$.} The error bars mark the standard errors of the means.
    {\bf A--C.} Mean sample correlations (black) and mean partial correlations (red) estimated by $C_{\sf sparse+latent}$ across $n=5$ imaged sites. The values in each bin are normalized by the average across all pairs of their sites.
    {\bf A.} Mean sample correlations and partial correlations of the $C_{\sf sparse+latent}$ estimator between pairs of neurons tuned to orientation as a function of $\Delta ori$.
    {\bf B.} Mean sample correlations and mean partial correlations of the $C_{\sf sparse+latent}$ estimator between horizontally aligned pairs of neurons ($\Delta z<30\,\mu$m) as a function of $\Delta x$.
    {\bf C.} Mean sample correlations and mean partial correlations of the $C_{\sf sparse+latent}$ estimator between vertically aligned pairs of neurons ($\Delta x<30\,\mu$m) as a function of $\Delta z$.
    {\bf D--F.} Mean positive connectivity (green) and mean negative connectivity (dark red) inferred by the $C_{\sf sparse+latent}$ estimator in $n=5$ imaged sites. Positive connectivity in each condition is computed as the fraction of positive partial correlations in the sparse component of the partial correlation matrix meeting the condition normalized by the connectivity in entire site (See \figref{5}{B}). Similarly, negative connectivity is the fraction of negative partial correlations similarly conditioned and normalized.
    {\bf D.} Positive connectivity decreases with $\Delta ori$ whereas negative connectivity does not.
    {\bf E.} Positive connectivity decays with $\Delta x$ whereas negative connectivity does not. 
    {\bf F.} Positive connectivity decays with $\Delta z$. Negative connectivity does not decay for small values of $\Delta z$.
    }
\label{fig:6}
\end{figure}

\section*{Discussion}
\paragraph{Functional connectivity as a network of pairwise interactions}
Functional connectivity is often represented as a graph of pairwise interactions. The goal of many studies of functional connectivity has been to estimate  anatomical connectivity from  observed multineuronal spiking activity.  For example, characteristic peaks and troughs in the pairwise cross-correlograms of recorded spike trains contain statistical signatures of directional monosynaptic connections and shared synaptic inputs \cite{Gerstein:1964, Perkel:1967, Moore:1970, Alonso:1998, Denman:2013}.  Such signatures are ambiguous as they can arise from network effects other than direct synaptic connections \cite{Aertsen:1989}.  With simultaneous recordings from more neurons, ambiguities can be resolved by inferring the conditional dependencies between pairs of neurons.  Direct causal interactions between neurons produce statistical dependency between them even after conditioning on the state of the remainder of the network and external input. Therefore, conditionally independent neurons can be inferred to lack a direct causal influence.

@@

\paragraph{Model selection}
Various model selection criteria have been devised to take into account the quality of the fit of a given model and its complexity and to demonstrate which model serves as the best statistical description for observed data. Despite its high computational requirements, cross validation is among the most populate model selection methods due to its minimal assumptions about the data generating process \cite{Arlot:2010}.

@@

Distances between cells in physical space and in sensory feature space had a stronger effect on the partial correlations estimated by the $C_{\sf sparse+latent}$ estimator than on sample correlations (\figref{6}{A--C}). This difference in decay rates supports the idea that correlations are built up from partial correlations in chains of intermediate cells positioned closer and tuned more similarly to one another, with potentially closer correspondence to anatomical connectivity.  This effect may be at least partially explained by a trivial effect of regularization: $L_1$ penalty employed by the estimator (Eq.~\ref{eq:ma}) suppresses small partial correlations to greater extent than large partial correlations, enhancing the apparent effect of distance and tuning.  These distances also had distinctly different effects on the positive and negative connectivities inferred by the estimator (\figref{6}{D--F}); these differences are not explained by trivial numerical effects and may reflect geometric and graphical features of local excitatory and inhibitory networks. Indeed, the relationships between patterns of positive and negative connectivities inferred by the estimator mirrored some regularities in studies of excitatory and inhibitory synaptic connectivities with respect to distance, cortical layers, and feature tuning \cite{Song:2005, Oswald:2008, Adesnik:2010, Perin:2011, Fino:2011, Hofer:2011, Isaacson:2011, Levy:2012}. For example, while excitatory neurons form synapses within highly specific local cliques \cite{Perin:2011}, inhibitory interneurons form synapses with nearly all excitatory cells within local microcircuits \cite{Fino:2011, Hofer:2011, Packer:2011}.  To further investigate the link between synaptic connectivity and inferred functional connectivity, future experiments will utilize molecular markers for different cell types with follow-up multiple whole-cell \emph{in vitro} experiments \cite{Hofer:2011, Ko:2013} to directly compare the inferred functional connectivity graphs to the underlying anatomical circuitry. Finally, the latent units inferred by the estimator can be analyzed for their physiological interpretation. For example, these latent units may be modulated under different brain states (e.g. slow-wave sleep, attention) and stimulus conditions (e.g. certain types of stimuli may engage feedback connections).

>>>>

Improved estimation of the correlation matrix is beneficial in itself. For example, improved estimates can be used to optimize  decoding of the population activity \cite{Friedman:1989}. But reduced estimation error is not the only benefit of regularization.  Finding the most efficient among many regularized estimators leads to insights about the system itself: the structure of the most efficient estimator is a parsimonious representation of the regularities in the data.

@@

Given a set of observations $\{x(t): t\in T$\} of population activity, where $x(t)$ is a $p\times 1$ vector of firing rates in time bin $t$, and an independent unbiased estimate $\bar x$ of the mean activity, the \emph{sample covariance matrix},
\begin{equation}\label{eq:sample}
	C_{\sf sample} = \frac 1 n \sum\limits_{t\in T} (x(t)-\bar x)(x(t)-\bar x)^\T,
\end{equation}
where $n$ is the size of $T$, yields an unbiased estimate of the covariance matrix so that $\E{C_{\sf sample}}=\Sigma$.

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics{./figures/Figure01.pdf}
    \end{center}
    \caption{{\bf Regularized estimators whose structure matches the true structure in the data are more efficient.}
    {\bf Row 1.} Graphical representations of the target estimates of the four respective regularized covariance matrix estimators.  Recorded neurons are represented by green spheres and latent units by light-shaded spheres.  Edges represent non-zero partial correlations, \ie \sq{interactions}.
        {\bf Row 1, A}.  For estimator $C_{\sf diag}$, the target estimate is a diagonal matrix, which describes systems that lack linear dependencies. 
        {\bf  Row 1, B.} For estimator $C_{\sf factor}$, the target estimate is a factor model (low-rank matrix plus a diagonal matrix), representing systems in which correlations arise due to common input from latent units. 
        {\bf  Row 1, C}. For estimator $C_{\sf sparse}$, the covariance matrix is approximated as the inverse of a sparse matrix. This approximation describes systems in which correlations arise from a sparse set of  linear associations between the observed units. 
        {\bf  Row 1, D}.  For estimator $C_{\sf sparse+latent}$, the covariance matrix is approximated as the inverse of the sum of a sparse matrix and a low-rank matrix. This approximation describes a model wherein correlations arise due to sparse associations between the recorded cells \emph{and} with several latent units. \\
{\bf Row 2:} Examples of $50\times 50$ correlation matrices corresponding to each structure: {\bf A.} the diagonal correlation matrix, {\bf B.} a factor model with four latent units, {\bf C.}  a correlation matrix with 67\%  off-diagonal zeros in its inverse, and {\bf  D.} a correlation matrix whose inverse is the sum of a rank-3 (\ie three latent units) matrix and a sparse matrix with 76\% off-diagonal zeros. 
\\
{\bf Row 3:} Sample correlation matrices calculated from samples of size $n=500$ drawn from simulated random processes with respective correlation matrices shown in Row 2.  The structure of the sample correlation matrix is difficult to discern.
\\
{\bf Row 4:} Correlation matrix estimates computed by estimators with matching structure from the same data as the sample correlation matrices in Row 3. The regularized estimates are closer to the truth than the sample correlation matrices.
\\
{\bf Row 5:} Excess losses (Eq.~\ref{eq:loss}) for the five estimators as a function of sample size. The error bars indicate the standard error of the mean based on 30 samples.  Estimators with structure that matches the true model converged to zero faster than the other estimators. Some exceptions occur when the sample is too small to reveal the structure in the data. In these cases estimators with simpler structures can be more efficient than estimators with true structure.
\\
{\bf Row 6:} Validation losses for the five estimators relative to the matching estimator. Error bars indicate the standard error of the mean based on 30 samples.
    }
    \label{fig:1}
\end{FPfigure}

@@

We drew 30 independent samples of sizes $n=250$, 500, 1000, 2000, and 4000 from each model and computed the \emph{excess loss} $\loss{C,\Sigma}-\loss{\Sigma,\Sigma}$ for each of the five estimators.  The hyperparameters of the regularized estimators were optimized by nested cross-validation using only the data in the sample.  All the regularized estimators produced better estimates (lower excess loss) than the sample covariance matrix.  However, estimators whose structure matched the true model outperformed the other estimators (\figref{1}{\,Row 5}).  Note that when the ground truth had zero correlations (Column A), $C_{\sf factor}$ performed equally well to $C_{\sf diag}$ because it correctly identified zero factors and only estimated the individual variances. Similarly, when the number of latent units was zero (Column C), $C_{\sf sparse+latent}$ performed equally well to $C_{\sf sparse}$ because it correctly identified zero latent units.

@@

To test this hypothesis, we computed the relative cross-validation loss of estimators  $C_{\sf sample}$, $C_{\sf diag}$, $C_{\sf factor}$, and $C_{\sf sparse}$ with respect to $C_{\sf sparse+latent}$ in $n=27$ imaged sites in 14 mice.  The hyperparameters of each estimator were optimized by nested cross-validation (See Methods). Indeed, the sparse+latent estimator outperformed the other estimators (Fig.~\ref{fig:3}). The respective median differences of the cross-validation loss were 0.039, 0.0016, 0.0029, and 0.0059 nats/cell/bin, significantly greater than zero ($p<0.01$ in each comparison, $n=27$ sites in 14 mice, Wilcoxon signed rank test).

@@

First, we analyzed how correlations and connectivity depended on the difference in preferred orientations ($\Delta ori$) of pairs of significantly ($\alpha=0.05$) tuned cells. The partial correlations decayed more rapidly with $\Delta ori$ than did sample correlations ($p<10^{-9}$ in each of the five sites, two-sample $t$-test of the difference of the linear regression coefficients). Positive connectivity decreased with $\Delta ori$ ($p<0.005$ in each of the five sites, $t$-test on the logistic regression coefficient) whereas negative connectivity did not decrease (\figref{6}{D}): The slope in the logistic model of connectivity with respect to $\Delta ori$ was significantly higher for positive than for negative interactions ($p<0.04$ in each of the five sites, two-sample $t$-test of the difference of the logistic regression coefficient).

Second, we compared how correlations and connectivity depended on the physical distance separating pairs of cells. We distinguished between lateral distance, $\Delta x$, in the plane parallel to the pia, and vertical distance, $\Delta z$, orthogonal to the pia.  When considering the dependence on $\Delta x$, the analysis was limited to cell pairs located at the same depth with $\Delta z < 30\,\mu\mbox{m}$; conversely, when considering the dependence on $\Delta z$, only vertically aligned cell pairs with $\Delta x < 30\,\mu\mbox{m}$ were included. Again, the partial correlations decayed more rapidly both laterally and vertically than sample correlations ($p<10^{-6}$ in each of the five sites, for both lateral and vertical distances, two-sample $t$-test of the difference of the linear regression coefficients). 
Positive connectivity decayed with distance ($p<10^{-6}$ in each of the five sites for positive interactions and $p<0.05$ for negative interactions, $t$-test on the logistic regression coefficient) (\figref{6}{E}), so that cells separated laterally by less than 25 $\mu\mbox{m}$ were 3.2 times more likely to be connected than cells separated laterally by more than 150 $\mu\mbox{m}$. Although the positive connectivity appeared to decay faster with vertical than with lateral distance, the differences in slopes of the respective logistic regression models were not significant with available data. The negative connectivity decayed slower with distance in the available range (\figref{6}{E and F}): The slope in the respective logistic models with respect to the lateral distance was significantly higher for positive than for negative connectivities ($p<0.05$ in each of the five sites, two-sample $t$-test of the difference of the logistic regression coefficients).

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure06.pdf}
    \end{center}
    \caption{{\bf Dependence of sample correlations, regularized partial correlations, and inferred connectivity of the $C_{\sf sparse+latent}$ estimator on the differences in preferred orientations, $\Delta ori$, and physical distances, $\Delta x$ and $\Delta z$.} The error bars mark the standard errors of the means.
    {\bf A--C.} Normalized mean sample correlations (black) and normalized mean partial correlations (red) estimated by $C_{\sf sparse+latent}$ across $n=5$ imaged sites. The values in each bin are normalized by the means across the entire site, which are shown in \figref{5}{C}, to make the effects more comparable across the sites.
    {\bf A.} Normalized mean sample correlations and normalized mean partial correlations of the $C_{\sf sparse+latent}$ estimator between pairs of neurons tuned to orientation as a function of $\Delta ori$.
    {\bf B.} Normalized mean sample correlations and normalized mean partial correlations of the $C_{\sf sparse+latent}$ estimator between horizontally aligned pairs of neurons ($\Delta z<30\,\mu$m) as a function of $\Delta x$.
    {\bf C.} Normalized mean sample correlations and normalized mean partial correlations of the $C_{\sf sparse+latent}$ estimator between vertically aligned pairs of neurons ($\Delta x<30\,\mu$m) as a function of $\Delta z$.
    {\bf D--F.} Normalized positive connectivity (green) and normalized negative connectivity (dark red) inferred by the $C_{\sf sparse+latent}$ estimator in $n=5$ imaged sites. Normalized positive connectivity in each condition is computed as the fraction of positive partial correlations in the sparse component of $C_{\sf sparse+latent}$ for each category of cell pairs, normalized by the connectivities across the entire sites, which are shown in \figref{5}{B}. Similarly, normalized negative connectivity is the fraction of negative partial correlations similarly conditioned and normalized. The normalization made the effects more comparable across sites.
    {\bf D.} Positive connectivity decreases with $\Delta ori$ whereas negative connectivity does not.
    {\bf E.} Positive connectivity decays with $\Delta x$ whereas negative connectivity does not. 
    {\bf F.} Positive connectivity decays with $\Delta z$. Negative connectivity does not decay for small values of $\Delta z$.
    }
\label{fig:6}
\end{figure}

\section*{Discussion}
\paragraph{Functional connectivity as a network of pairwise interactions}
Functional connectivity is often represented as a graph of pairwise interactions. The goal of many studies of functional connectivity has been to estimate  anatomical connectivity from  observed multineuronal spiking activity.  For example, characteristic peaks and troughs in the pairwise cross-correlograms of recorded spike trains contain statistical signatures of directional monosynaptic connections and shared synaptic inputs \cite{Gerstein:1964, Perkel:1967, Moore:1970, Alonso:1998, Denman:2013}.  Such signatures are ambiguous as they can arise from network effects other than direct synaptic connections \cite{Aertsen:1989}.  With simultaneous recordings from more neurons, ambiguities can be resolved by inferring the conditional dependencies between pairs of neurons.  Direct causal interactions between neurons produce statistical dependency between them even after conditioning on the state of the remainder of the network and external input. Therefore, conditional independence can signify the absence of a direct causal influence.

@@

\paragraph{Model selection}
Various model selection criteria have been devised to select between families of models and the optimal subset of variables in a given model family based on observed data. Despite its high computational requirements, cross validation is among the most popular model selection methods due to its minimal assumptions about the data generating process \cite{Arlot:2010}.

@@

Distances between cells in physical space and in sensory feature space had a stronger effect on the partial correlations estimated by the $C_{\sf sparse+latent}$ estimator than on sample correlations (\figref{6}{A--C}). 
These differences support the idea that correlations are built up from partial correlations in chains of intermediate cells positioned closer and tuned more similarly to one another, with potentially closer correspondence to anatomical connectivity.  These differences may also be at least partially explained by a trivial effect of regularization: $L_1$ penalty employed by the estimator (Eq.~\ref{eq:ma}) suppresses small partial correlations to greater extent than large partial correlations, enhancing the apparent effect of distance and tuning.  Distances between cells in physical space and in sensory feature space also had distinct effects on the positive and negative connectivities inferred by the estimator (\figref{6}{D--F}); we could not think of a numerical artifact that could produce this effect. The distinct positive and negative connectivity patterns  may reflect geometric and graphical features of local excitatory and inhibitory networks. Indeed, the relationships between patterns of positive and negative connectivities inferred by the estimator mirrored some regularities in studies of excitatory and inhibitory synaptic connectivities with respect to distance, cortical layers, and feature tuning \cite{Song:2005, Oswald:2008, Adesnik:2010, Perin:2011, Fino:2011, Hofer:2011, Isaacson:2011, Levy:2012}. For example, while excitatory neurons form synapses within highly specific local cliques \cite{Perin:2011}, inhibitory interneurons form synapses with nearly all excitatory cells within local microcircuits \cite{Fino:2011, Hofer:2011, Packer:2011}.  To further investigate the link between synaptic connectivity and inferred functional connectivity, in future experiments, we will use molecular markers for various cell types with follow-up multiple whole-cell \emph{in vitro} experiments \cite{Hofer:2011, Ko:2013} to directly compare the inferred functional connectivity graphs to the underlying anatomical circuitry. Finally, the latent units inferred by the estimator can be analyzed for their physiological interpretation. For example, these latent units may be modulated under different brain states (e.g. slow-wave sleep, attention) and stimulus conditions (e.g. certain types of stimuli may engage feedback connections).
